Timely Object Recognition

### 2012-03-05 writeups/eccv12/introduction.tex

In recent years, the computer vision field has converged on a general method for object detection, and a standard evaluation of results.
Most current state-of-the-art object detection systems consist of three tasks: proposing regions of the image, evaluating a given region for presence of an object of a given category, and post-processing the results.
In the evaluation ground truth, each object is most commonly assumed to belong to one of a fixed set of classes; its location is approximated by placing a bounding box around pixels belonging to it.
Large datasets of such human annotations are used for evaluation of detection algorithms~\cite{pascal-voc-2010}.

@@

@@

\begin{figure}[ht!]
\center{\includegraphics[width=0.56\linewidth]
    {figures/evaluation.pdf}}
  \caption{We aim for \emph{Anytime} performance within the bounds of the curve. That is, the policy should give the best possible answer at any time from start time $T_s$ to deadline $T_d$.}
  \label{fig:evaluation}
\end{figure}

@@

A hypothetical recognition system for an advertising deployment presents a great case study.
The system will have different accuracies for objects of different classes; detections will have different values based on confidence and class; and the queue of unprocessed images will vary in size.
The most rational detection strategy in such an environment should depend on all of these variables.

@@

Our goal is a dynamic policy for selecting classifiers or detectors to achieve the highest recognition performance under this evaluation.
Without further ado, let us formalize the problem.

>>>>

In recent years, the computer vision field has converged on a general method for object detection, and a standard evaluation of results.
Most current state-of-the-art object detection systems consist of three tasks: proposing regions of the image, evaluating a given region for presence of an object of a given category, and post-processing the results.
In the evaluation ground truth, each object is most commonly assumed to belong to one of a fixed set of classes; its location is approximated by placing a bounding box around pixels belonging to it.
Large datasets of such human annotations are used for evaluation of detection algorithms~\cite{pascal-voc-2010,imagenet_cvpr09}.

@@

\begin{figure}[ht!]
\center{\includegraphics[width=0.56\linewidth]
    {figures/evaluation.pdf}}
  \caption{We aim for \emph{Anytime} performance within the bounds of the curve. That is, the policy should give the best possible answer at any time from start time $T_s$ to deadline $T_d$. \todo{CAN WE PUT PICTURES OF DETECTORS IN HERE?}}
  \label{fig:evaluation}
\end{figure}

@@

@@

A hypothetical recognition system for a vision-based advertising deployment presents a case study.
The system will have different accuracies for objects of different classes; detections will have different values based on confidence and class; and the queue of unprocessed images will vary in size.
The most rational detection strategy in such an environment should depend on all of these variables.

@@

Our goal is a dynamic policy for selecting classifiers or detectors to achieve the highest recognition performance under this evaluation.

### 2012-03-05 writeups/eccv12/technical.tex

As presented in Figure~\ref{fig:pomdp}, our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and outputs $\{\emph{classify}(1), \dots, \emph{classify}(K)\}$ and a list of multi-class detection results $\emph{detect}(I)$.

@@

Remember that our heuristic value function consisted of picking the action corresponding to the class presence variable with the highest probability $P(C_k)$.
We can formulate such a policy as a scalar product:
\begin{align}
\pi(b) = \argmax_{a_i \in \mathcal{A}} \theta^\top \phi(b,a_i)
\end{align}
where $\phi(b,a_i)$ is a feature vector representation of the belief state.
This approach is known as function approximation in reinforcement learning \cite{Sutton1998}.

@@

One feature we want the reward function to have is additivity.
Let's say that given deadline $T_d$ and some image, the policy had time to take $J$ actions.
The total reward of a policy $\pi$ starting at state $b^j$ is then defined as the sum of rewards
\begin{equation}
R(h^j) = \sum_{j'=j}^J R(b_j')
\end{equation}

@@

The feature representation of the belief state for a given action $a_i$ that corresponds to class $k$ is defined to be
\begin{align}
[P(C_k), \, H(C_k), \, 1]
\end{align}

@@

With this policy, we run $N$ recognition episodes.
From the state-action samples gathered in running the episodes, we formulate a matrix $\Phi$ from the featurizations $\phi(b^j,a_i)$, and a vector $y$ consisting of the individual rewards $R(b^j,a_i)$.
We then solve the system $\Phi \theta = y$.

\todo{more}

>>>>

As presented in Figure~\ref{fig:pomdp}, our goal is a multi-class recognition policy $\pi$ that takes an image $\mathcal{I}$ and then outputs $\{\emph{classify}(1), \dots, \emph{classify}(K)\}$ and a list of multi-class detection results $\emph{detect}(I)$.

@@

Remember that our heuristic value function consisted of picking the action corresponding to the class presence variable with the highest probability $P(C_k)$.
We can formulate such a policy as a scalar product:
\begin{align}
\pi(b) = \argmax_{a_i \in \mathcal{A} \setminus \mathcal{O}} \theta^\top \phi(b,a_i)
\end{align}
where $\phi(b,a_i)$ is a feature vector representation of the belief state.
This approach is known as function approximation in reinforcement learning \cite{Sutton1998}.

@@

One feature we want the reward function to have is additivity.
Let's say that given deadline $T_d$ and some image, the policy had time to take $J$ actions.
The total reward of a policy $\pi$ starting at state $b^j$ is then defined as the sum of rewards
\begin{equation}
R(h^j) = \sum_{j'=j}^J R(b_j',a^{j'})
\end{equation}

@@

The feature representation of the belief state for a given action $a_i$ that corresponds to class $k$ is defined to be
\begin{align}
\phi_k(b) = [P(C_k), \, H(C_k), \, 1]
\end{align}

@@

With this policy, we run $N$ recognition episodes.
From the state-action samples gathered in running the episodes, we formulate a matrix $\Phi$ from the featurizations $\phi(b^j,a_i)$, and a vector $y$ consisting of the individual rewards $R(b^j,a_i)$.

The rewards are computed as the sum of discounted rewards to the end of the episode:
\begin{align}
R(b^j,a_i) = \sum_{i=0}^{J-j} \lambda^i R(b_{j+i},a^{j+i})
\end{align}
Note that with $\lambda=0$, the reward is determined entirely by the actual action taken; with $\lambda=1$, the reward is the sum of all rewards until the end of the episode.

We then solve the system $\Phi \theta = y$ for $\theta$ with Lasso regression.
With the updated weights $\theta$, we run $N$ more episodes and repeat the procedure until convergence.

The parameters of this training procedure are the $\alpha$ weight on the regularization term in the regression and the $\lambda$ discount weight.
We cross-validate for both values.
